\documentclass{beamer}
\mode<presentation>
\usepackage[utf8]{inputenc}
\usepackage[brazilian]{babel}
\usepackage{multirow}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage[ruled,lined,portuguese]{algorithm2e}
\usepackage{subfig}

\AtBeginSection[]
{
    \begin{frame}
        \frametitle{Sumário}
        \tableofcontents[currentsection]
    \end{frame}
}

\title{Implantação e Avaliação de um Algoritmo de Ranking Baseado em Classificação}
\author{Igor Giusti}

\begin{document}

\frame{\titlepage}

\begin{frame}
    \frametitle{Sumário}
    \tableofcontents
\end{frame}

\section{Introdução}
\input{introduction}

\section{Ranking: Noções Preliminares}
\input{ranking.preliminaries}

\section{Ranking: Implantação}
\input{ranking}

\section{Ranking: Resultados e Avaliação}
\input{results.and.evaluation}

\section{Conclusão}
\input{conclusion}

\begin{frame}
    \frametitle{REFERÊNCIAS BIBLIOGRÁFICAS}

    \begin{enumerate}
        \item BALCAN, M.-F. et al. Robust reductions from ranking to classification. In: Proceedings of 20th annual conference on Learning theory. [S.l.: s.n.], 2007.
        \item WITTEN, I. H.; FRANK, E. Data Mining: Practical Machine Learning Tools and Techniques. 2nd edition. [S.l.]: Morgan Kaufmann, 2005.
        \item LIU, T.-Y. Learning to rank for information retrieval. Foundations and Trends in Information Retrieval, v. 3, n. 3, 2009.
        \item AILON, N.; MOHRI, M. An efficient reduction of ranking to classification. In: In Conference on Learning Theory (COLT). [S.l.: s.n.], 2008.
        \item GUO, H. Learning from imbalanced data sets with boosting and data generation: The databoost-im approach. SIGKDD Explorations, v. 6, p. 2004, 2004.
    \end{enumerate}
\end{frame}

\begin{frame}
    \centering
    FIM.

    Obrigado!
    
    Duvidas?

\end{frame}

\end{document}
